---
pagetitle: "Adrián Cidre | Courses"
title: ""
execute: 
  echo: false
  freeze: false
---

```{r functions}
source("assets/scripts/00_courses.R")
```

::::: {.column-screen .jumbotron .jumbotron-courses .d-none .d-sm-block}
<div>

## Courses of R and GIS {.text-black .jumbotron-title}

</div>

::: jumbotron-text
Learn data analysis and geographic information systems (GIS) with R — with me as your guide! Choose from courses available in Spanish or English on the Udemy platform. Once you purchase a course, you’ll have lifetime access, so you can learn at your own pace.
:::
:::::

:::: {.row .d-block .d-sm-none}
::: {.card .card-courses}
## Courses

Learn data analysis and geographic information systems (GIS) with R — with me as your guide! Choose from courses available in Spanish or English on the Udemy platform. Once you purchase a course, you’ll have lifetime access, so you can learn at your own pace.
:::
::::

## Coupons informacion {.course-description}

My courses are offered through a third party that hosts the material. You have two main options to purchase the course:

-   **If you buy it directly from the links I offer you** **in this webpage**: I get most of the revenue for the sale, and that helps me to continue adding new content, and new courses.

-   **If you buy it through the Udemy site**: you get the exact same course, sometimes for the same price, sometimes for a higher price, and I get only 33% of the money you pay, while Udemy gets 67%.

<!-- I have to update the coupons manually, therefore, it's very likely that I will forget to update them sometimes. If the coupons don't work, leave me a comment below and I will update them as soon as possible. The duration of the coupons depends on Udemy: -->

<!-- -   Price 9.99€: the coupons will last for 5 days -->

<!-- -   Price 12.99€: the coupons will last for 30 days -->

::::: {.container .grid .mt-5}
::: {.g-col-12 .g-col-md-6}
I have to update the coupons manually, therefore, it's very likely that I will forget to update them sometimes. If the coupons don't work, leave me a comment below and I will update them as soon as possible. The duration of the coupons depends on Udemy:

-   Price 9.99€: the coupons will last for 5 days

-   Price 12.99€: the coupons will last for 30 days
:::

::: {.g-col-12 .g-col-md-6}
```{r}
offer_card
```
:::
:::::

## Courses {.course-description}

::::::::: {.container .grid .mt-5}
::: {.g-col-12 .g-col-md-6}
```{r}
course_card(
  file         = "assets/figures/00_course_figures/04_best_r_practices.png",
  course_title = "Mastering R: Best Practices and Essential Tools",
  mode         = "Online",
  # date         = "Available Anytime",
  time         = "20 hours",
  language     = "English",
  href         = "courses/05_best_r_practices.qmd"
)
```
:::

::: {.g-col-12 .g-col-md-6}
```{r}
course_card(
  file         = "assets/figures/00_course_figures/05_spatial_ecology.png",
  course_title = "Ecología espacial aplicada en R",
  mode         = "Online",
  # date         = "16/Feb - 21/Mar",
  time         = "30 horas",
  language     = "Español",
  href         = "courses/04_spatial_ecology_es.qmd"
)
```
:::

::: {.g-col-12 .g-col-md-6}
```{r}
course_card(
  file         = "assets/figures/00_course_figures/03_intro_spatial_data.png",
  course_title = "Introducción a Análisis de Datos Espaciales en R",
  mode         = "Online",
  # date         = "Available Anytime",
  time         = "40 horas",
  language     = "Español",
  href         = "courses/02_spatial_data_es.qmd"
)
```
:::

::: {.g-col-12 .g-col-md-6}
```{r}
course_card(
  file         = "assets/figures/00_course_figures/03_intro_spatial_data.png",
  course_title = "Introduction to Spatial Data Analysis with R",
  mode         = "Online",
  # date         = "Available Anytime",
  time         = "40 hours",
  language     = "English",
  href         = "courses/03_spatial_data_en.qmd"
)
```
:::

::: {.g-col-12 .g-col-md-6}
```{r}
course_card(
  file         = "assets/figures/00_course_figures/02_analisis_datos.png",
  course_title = "Introducción a Análisis y Visualización de datos en R",
  mode         = "Online",
  time         = "30 horas",
  language     = "Español",
  href         = "courses/01_data_analysis_es.qmd"
)
```
:::

::: {.g-col-12 .g-col-md-6}
```{r}
course_card(
  file         = "assets/figures/00_course_figures/01_quarto.png",
  course_title = "Literate programming y Automatización con Quarto en R",
  mode         = "Online",
  time         = "20 horas",
  language     = "Español",
  href         = "courses/00_quarto_es.qmd"
)
```
:::
:::::::::

<br>


{{< include assets/includes/buymeacoffee.qmd >}}
