---
title: "Introduction to Spatial Data Analysis and GIS in R"
title-block-banner: true
execute: 
  echo: false

# Comments section
comments: 
  utterances: 
    repo:  Cidree/blogComments
---

```{r}
source("../03_scripts/00_courses.R")
```

::: course-banner
```{r}
course_banner(
  price    = "13 €",
  mode     = "Online",
  time     = "30 hours",
  date     = "Available Anytime",
  img_file = "../01_figures/00_course_figures/03_intro_spatial_data.png"
)
```
:::

::: course-link
```{r}
a(class = "text-center btn btn-success course-link--button",
  target = "_blank",
  href = "https://www.udemy.com/course/introduction-to-spatial-data-analysis-and-gis-in-r/?couponCode=E519DBA154370760A8E6",
  "Enroll to the course")
```
:::

::: course-description
::: course-description--title
## Introduction to the Course
:::
:::

{{< video https://www.youtube.com/watch?v=FSE_VnJuTFw >}}

::: course-description
::: course-description--title
## Description
:::

::: course-description--text
Welcome to my Spatial Data Analysis course in R!

This course is designed for beginners and intermediate-level individuals who want to learn everything necessary about spatial data analysis using the R programming language. We will focus on the most current packages and practices for working with real spatial data. In total, we will use 27 different R packages, making it an intense but very comprehensive course.

Here below is an example of what you will learn to perform in this course:
:::
:::

```{=html}
<iframe src="../01_figures/01_html/population_spain.html" width="800" height="600"></iframe>
```
::: course-description
::: course-description--title
## Prerequisites
:::

::: course-description--text
-   Basic knowledge of R

-   To be familiar with tidyverse functions, including basic graphics with ggplot2 and pipelines
:::
:::

::: {.course-curriculum .column-screen}
::: course-description--title
## Course Contents
:::

```{r}
# Introducción --------------------------------------------------------------------
course_block(
  section_name = "Introduction",
  id_accordion = "acc_qes_01",
  id_heading   = "head_qes_01",
  id_collapse  = "col_qes_01",
  
  strong("Introduction to the course"),
  tags$ul(
    tags$li("Introduction to the course"),
    tags$li("Environment set-up"),
    tags$li("Course materials")
  )
)

# 01. Introduccion datos espaciales ---------------------------
course_block(
  section_name = "SECTION 01 - Introduction to Spatial Data",
  id_accordion = "acc_qes_02",
  id_heading   = "head_qes_02",
  id_collapse  = "col_qes_02",
  
  ## Theory
  strong("Theory"),
  tags$ul(
    tags$li("Spatial data vs Non-spatial data"),
    tags$li("Geometries in vector data"),
    tags$li("Simple features"),
    tags$li("Common formats"),
    tags$li("QUIZ 1")
  ),
  
  ## Practice
  strong("Practice"),
  tags$ul(
    tags$li("Download spatial data"),
    tags$li("Exploratory data analysis"),
    tags$li("Import/Export spatial data"),
    tags$li("Properties of vector data")
  ),
  
  ## Challenge
  strong("Challenge 01")
)

# 02. CRS  --------------------------------------------------
course_block(
  section_name = "SECTION 02 - Coordinate Reference Systems",
  id_accordion = "acc_qes_03",
  id_heading   = "head_qes_03",
  id_collapse  = "col_qes_03",
  
  ## Theory
  strong("Theory"),
  tags$ul(
    tags$li("Importance of CRS"),
    tags$li("CRS, coordinates, georeferencing"),
    tags$li("Geographic CRS vs Projected CRS"),
    tags$li("Projections"),
    tags$li("EPSG codes, proj4, WKT ..."),
    tags$li("QUIZ 2")
  ),
  
  ## Practice
  strong("Practice"),
  tags$ul(
    tags$li("Explore CRS"),
    tags$li("CRS transformation"),
    tags$li("Assigning CRS"),
    tags$li("On-the-fly transformations"),
    tags$li("First web map")
  ),
  
  ## Challenge
  strong("Challenge 02")
)

# 03. Geometric Operations ---------------------------------------
course_block(
  section_name = "SECTION 03 - Geometric Operations",
  id_accordion = "acc_qes_04",
  id_heading   = "head_qes_04",
  id_collapse  = "col_qes_04",
  
  ## Theory
  strong("Theory"),
  tags$ul(
    tags$li("Spatial predicates"),
    tags$li("Geometry measures"),
    tags$li("Unary transformations"),
    tags$li("Binary transformations"),
    tags$li("Other operations"),
    tags$li("QUIZ 3")
  ),
  
  ## Practice
  strong("Practice"),
  tags$ul(
    tags$li("Predicate functions for counting elements"),
    tags$li("Spatial filters"),
    tags$li("Spatial joins"),
    tags$li("Spatial measurements"),
    tags$li("Transformations (centroid, buffer ...)"),
    tags$li("Download map of Spain from R")
  ),
  
  ## Challenge
  strong("Challenge 03")
)

# 04. Raster Data ---------------------------------------
course_block(
  section_name = "SECTION 04 - Raster Data",
  id_accordion = "acc_qes_05",
  id_heading   = "head_qes_05",
  id_collapse  = "col_qes_05",
  
  ## Theory
  strong("Theory"),
  tags$ul(
    tags$li("Definition of raster data"),
    tags$li("Types of resolution"),
    tags$li("Introduction to remote sensing"),
    tags$li("Common operations"),
    tags$li("Calculation of vegetation indices (NDVI, SAVI)"),
    tags$li("QUIZ 4")
  ),
  
  ## Practice
  strong("Practice"),
  tags$ul(
    tags$li("Explore raster data"),
    tags$li("Download Digital Elevation Model (DEM)"),
    tags$li("Raster derivatives from DEM"),
    tags$li("Common operations (cutting, reclassifying ...)"),
    tags$li("Arithmetic operations with raster"),
    tags$li("Calculation of vegetation indices (NDVI, SAVI)"),
    tags$li("Generate RGB and false-color compositions")
  ),
  
  ## Challenge
  strong("Challenge 04")
)

# 05. Maps  --------------------------------------------
course_block(
  section_name = "SECTION 05 - Maps with ggplot2",
  id_accordion = "acc_qes_06",
  id_heading   = "head_qes_06",
  id_collapse  = "col_qes_06",
  
  strong("Maps"),
  tags$ul(
    tags$li("Population of Spain by municipalities"),
    tags$li("Brown bear in Picos de Europa I"),
    tags$li("Brown bear in Picos de Europa II"),
    tags$li("Rivers of Galicia"),
    tags$li("Andean bear in Peru"),
    tags$li("Severity of fire in Tenerife (2023)")
  )
)

# 06. Web Maps -----------------------------------------
course_block(
  section_name = "SECTION 06 - Web Maps with mapview",
  id_accordion = "acc_qes_07",
  id_heading   = "head_qes_07",
  id_collapse  = "col_qes_07",
  
  strong("Web Maps"),
  tags$ul(
    tags$li("Population of Spain by municipalities"),
    tags$li("Brown bear in Picos de Europa"),
    tags$li("Rivers of Galicia"),
    tags$li("Andean bear in Peru"),
    tags$li("Severity of fire in Tenerife (synchronized)"),
    tags$li("Severity of fire in Tenerife (side by side)")
  )
)

```
:::

::: course-description
::: course-description--title
## What's inside the course
:::

::: course-description--text
-   150 lessons

-   15 hours of video

-   All the course materials

-   Theoretical classes, practical sessions, quizzes, and proposed exercises

-   Additional bibliography

-   Fast answer to any student's question
:::
:::

::: course-description
::: course-description--title
## Course Results
:::

::: course-description--text
-   Analyzing vector data and raster data

-   Downloading spatial data in R

-   Common operations on vector data and raster data

-   Georeferencing data

-   CRS transformations

-   Creating stunning maps and web maps
:::
:::
