---
title: "Mastering R: Best Practices and Essential Tools"
title-block-banner: true
execute: 
  echo: false
format:
  html:
    grid: 
      sidebar-width: 100px
      margin-width: 100px
      body-width: 1000px
---

```{r}
source("../03_scripts/00_courses.R")
```

::: {.course-banner .column-screen}
```{r}
course_banner(
  price    = "12.99 €",
  mode     = "Online",
  time     = "15 hours",
  date     = "Available Anytime",
  img_file = "../assets/figures/00_course_figures/04_best_r_practices.png",
  lang     = "en"
)
```
:::

::: course-link
```{r}
a(class = "text-center btn btn-success course-link--button",
  target = "_blank",
  href = "https://www.udemy.com/course/mastering-r-best-practices-and-essential-tools/?couponCode=7F609688EA907615F173",
  "Enroll to the course")
```
:::

::: course-description
::: course-description--title
## Introduction to the Course
:::
:::

{{< video https://youtu.be/gc3PFF51Z7w >}}

::: course-description
::: course-description--title
## Description
:::

::: course-description--text
Welcome to Mastering R: Best Practices and Essential Tools!

In this course, we aim to address a significant gap in the market by equipping R users with the knowledge and skills needed to implement best practices. You will learn how to organize your projects effectively, adhere to the highest coding standards, and utilize a suite of powerful tools that will enhance your productivity and collaboration.

Our focus will be on providing you with practical, everyday techniques that streamline your workflow and make your code robust and shareable. By the end of this course, you'll be able to avoid the common pitfall of "this script works only on my machine" and ensure your projects are reproducible and portable.
:::
:::

::: course-description
::: course-description--title
## Prerequisites
:::

::: course-description--text
-   Basic/intermediate knowledge of R
:::
:::

::: {.course-curriculum .column-screen}
::: course-description--title
## Course Contents
:::

```{r}
# Section 01 - Introduction ----------------------
course_block(
  section_name = "Introduction",
  id_accordion = "acc_qes_01",
  id_heading   = "head_qes_01",
  id_collapse  = "col_qes_01",
  
  tags$ul(
    tags$li("Introduction to the course")
  )
)

# Section 02 - RStudio --------------------------
course_block(
  section_name = "Section 02 - RStudio IDE",
  id_accordion = "acc_qes_02",
  id_heading   = "head_qes_02",
  id_collapse  = "col_qes_02",

  tags$ul(
    tags$li("Setting up and navigating RStudio for an optimized coding environment"),
    tags$li("Work with RStudio projects"),
    tags$li("Essential shortcuts and tips")
  )
)

# Section 03 - Best coding practices ------------
course_block(
  section_name = "Section 03 - Best coding practices",
  id_accordion = "acc_qes_03",
  id_heading   = "head_qes_03",
  id_collapse  = "col_qes_03",

  tags$ul(
    tags$li("Learn to write clean, efficient and maintainable R code"),
    tags$li("Follow the tidyverse style guide")
  )
)

# Section 04 - Version control  ----------------
course_block(
  section_name = "Section 04 - Version control with Git and GitHub - Configuration",
  id_accordion = "acc_qes_04",
  id_heading   = "head_qes_04",
  id_collapse  = "col_qes_04",

  tags$ul(
    tags$li("Installation and setup of Git and GitHub"),
    tags$li("Generate 2 Factor Authentication")
  )
)

# Section 05 - Version control  ----------------
course_block(
  section_name = "Section 05 - Version control with Git and GitHub - Respositories",
  id_accordion = "acc_qes_05",
  id_heading   = "head_qes_05",
  id_collapse  = "col_qes_05",

  tags$ul(
    tags$li("Managing your code changes and collaborating with others using Git and GitHub"),
    tags$li("Learn different ways of creating and cloning repositories"),
    tags$li("Understand how privacy works"),
    tags$li("Git workflow"),
    tags$li("Reset, revert, restore"),
    tags$li("Working with branches"),
    tags$li("Collaboration with other people")
  )
)

# Section 06 - A real project  ----------------
course_block(
  section_name = "Section 06 - A real project",
  id_accordion = "acc_qes_06",
  id_heading   = "head_qes_06",
  id_collapse  = "col_qes_06",

  tags$ul(
    tags$li("Implement the previous learning in a real-world project")
  )
)


# Section 07 - Introduction to functional programming  ----------------
course_block(
  section_name = "Section 07 - Introduction to functional programming",
  id_accordion = "acc_qes_07",
  id_heading   = "head_qes_07",
  id_collapse  = "col_qes_07",

  tags$ul(
    tags$li("Concepts of functional programming"),
    tags$li("Create basic and advanded functions"),
    tags$li("Note on tidy evaluation"),
    tags$li("Iteration")
  )
)

# Section 08 - Functional programming in our real project  ------------
course_block(
  section_name = "Section 08 - Functional programming in our real project",
  id_accordion = "acc_qes_08",
  id_heading   = "head_qes_08",
  id_collapse  = "col_qes_08",

  tags$ul(
    tags$li("Change our real-world project to a project based in functional programming")
  )
)

# Section 09 - Reproducible environments  ------------
course_block(
  section_name = "Section 09 - Reproducible environments",
  id_accordion = "acc_qes_09",
  id_heading   = "head_qes_09",
  id_collapse  = "col_qes_09",

  tags$ul(
    tags$li("Creating reproducible R environments to ensure consistent project dependencies"),
    tags$li("Package vs library vs repository"),
    tags$li("Understand the concept of libraries and how they work"),
    tags$li("Computing environments with renv"),
    tags$li("Use of R installation manager")
  )
)


```
:::

::: course-description
::: course-description--title
## What's inside the course
:::

::: course-description--text
-   100 lessons

-   9 hours of video

-   Course materials

-   Fast answer to any student's question
:::
:::

::: course-description
::: course-description--title
## Course Results
:::

::: course-description--text
-   Use of RStudio efficiently

-   Write clean and maintainable code

-   Good level of use of Git and GitHub

-   Modularize projects using functional programming

-   Create reproducible environments with renv
:::
:::
